Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-21 cbm-rbd-paper.tex
other prior parameters

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau     & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / \tsysnow & \text{if } \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a timespan starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
\label{eq:gtnowtau}
\end{align}
and $\tausnow = \arg\min \gnow(\tau)$.
$\tausnow$, the optimal moment of maintenance as of $\tnow$,
incorporates thus all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
Figure~\ref{fig:ghistfig2} illustrates this procedure for a number of current times $\tnow$.

@@

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
These relations are depicted in Figure~\ref{fig:tauhistfig2}. %for a numerical example,

@@

\begin{figure}
\includegraphics[width=\textwidth]{ghistfig2}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout}
and prior component models as given in Table~\ref{tab:priorparams},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and costs $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghistfig2}
\end{figure}

@@

***example figures are with very weak prior info
(see Table~\ref{tab:priorparams}: $\nkz = 1$ or $2$),
things could look different for stronger expert information!

@@

\begin{table}
\centering
\begin{tabular}{crrrrrrr}
  \toprule
$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
  \midrule
M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
  \bottomrule
\end{tabular}
\caption{Prior parameters for the four component types as used in subsequent numerical examples.
The corresponding expected failure behaviour is visualized in Figure~\ref{fig:comppriorfig1}.}
\label{tab:priorparams}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{comppriorfig1}
\caption{Prior predictive reliability functions corresponding to the values from Table~\ref{tab:priorparams},
%for the four component types of the system depicted in Figure~\ref{fig:brakesys-layout},
showing the expected failure behaviour according to this choice of parameters.}
\label{fig:comppriorfig1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig2}
\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\cstarnow = \gnow(\tausnow)$,
and the total unit cost rate $\ctotalnow$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
at (absolute) time $8.5$.
Since $\tausnow$ does not change dramatically most of the time, $t^*$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
differing from the overall cost rate $\ctotalnow$ (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At time $8$, the overall expected cost rate for repair scheduled at time $8.38$ is $0.044$,
up from $0.036$ for repair scheduled at time $8.62$, as cost-optimal at time $7.9$.}
\label{fig:tauhistfig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig3}
\caption{Illustration of the gains due to the parameter update
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
same with $t^*$ (top right panel).
The adaptive algorithm recongnizes the higher reliability of system components,
leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
\label{fig:tauhistfig3}
\end{figure}

@@

***larger simulation study?

>>>>

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau     & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / \tsysnow & \text{if } \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a timespan starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
\label{eq:gtnowtau}
\end{align}
and $\tausnow = \arg\min \gnow(\tau)$.
$\tausnow$, the optimal moment of maintenance as of $\tnow$,
incorporates thus all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
Figure~\ref{fig:ghist1fig2} illustrates this procedure for a number of current times $\tnow$.

@@

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
These relations are depicted in Figure~\ref{fig:tauhist1fig2}. %for a numerical example,

@@

\begin{figure}
\includegraphics[width=\textwidth]{ghist1fig2}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout}
and prior component models as given in Table~\ref{tab:priorparams},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and costs $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghist1fig2}
\end{figure}

@@

***example figures are with very weak prior info
(see Table~\ref{tab:priorparams}: $\nkz = 1$ for all $k$),
things could look different for stronger expert information!

@@

\begin{table}
\centering
\begin{tabular}{crrrrrrr}
  \toprule
$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
  \midrule
% test prior
%M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
%H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
%C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
%P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
% prior 1
M & $2.5$ & $ 5$\rule{1.5ex}{0ex} & $244.1$ & $1$\rule{1ex}{0ex} \\
H & $1  $ & $10$\rule{1.5ex}{0ex} & $ 10.0$ & $1$\rule{1ex}{0ex} \\
C & $2  $ & $ 8$\rule{1.5ex}{0ex} & $ 11.5$ & $1$\rule{1ex}{0ex} \\
P & $1.5$ & $ 5$\rule{1.5ex}{0ex} & $ 13.0$ & $1$\rule{1ex}{0ex} \\
  \bottomrule
\end{tabular}
\caption{Prior parameters for the four component types as used in subsequent numerical examples.
The corresponding expected failure behaviour is visualized in Figure~\ref{fig:compprior1fig1}.}
\label{tab:priorparams}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{compprior1fig1}
\caption{Prior predictive reliability functions corresponding to the values from Table~\ref{tab:priorparams},
%for the four component types of the system depicted in Figure~\ref{fig:brakesys-layout},
showing the expected failure behaviour according to this choice of parameters.}
\label{fig:compprior1fig1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhist1fig2}
\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\cstarnow = \gnow(\tausnow)$,
and the total unit cost rate $\ctotalnow$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
$\tausnow$ (top left panel) first decreases, then starts to increase during failure-free periods,
dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
If $\tprep = 1$, the drop of $\tausnow$ from $1.43$ to $0.91$ at $\tnow = 4$ would trigger a maintenance action
at (absolute) time $5$.
Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
differing from the overall cost rate $\ctotalnow$ (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At time $4$, the overall expected cost rate for repair scheduled at time $4.91$ is $0.064$,
up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $3.9$.}
\label{fig:tauhist1fig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhist1fig3}
\caption{Illustration of the gains due to the parameter update
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
same with $\tstarnow$ (top right panel).
The adaptive algorithm recongnizes the higher reliability of system components,
leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
\label{fig:tauhist1fig3}
\end{figure}

%****************************

@@

%*******************************

larger simulation study?
